---
title: "SPECTRUM MSK Nichenet preprocessing"
author: "Florian Uhlitz"
date: "`r Sys.Date()`"
output: 
  html_document: 
    df_print: kable
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = F)

```

```{r chunk_010}

library(magrittr)
library(tidyverse)
library(Seurat)
library(readxl)
library(cowplot)
library(colorblindr)
library(viridis)
library(magick, lib.loc = "/home/uhlitzf/miniconda3/lib/R/library")
library(ggpubr)
library(nichenetr)

```

```{r chunk_030}

## load global vars: 
source("_src/global_vars.R")

# meta_tbl
# clrs
# markers_v7
# markers_v7_super
# cell_type_super_lookup


names(clrs$cell_type) <- str_replace_all(names(clrs$cell_type), "\\.", " ")
names(clrs$cell_type) <- str_replace_all(names(clrs$cell_type), "Ovarian", "Ov")

```


```{r chunk_040}

seu_cc <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/Ovarian.cancer.super_processed_filtered_annotated_sample.rds")
seu_tc <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/T.super_processed_filtered_annotated_sample.rds")
seu_ml <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/Myeloid.super_processed_filtered_annotated_sample.rds")
seu_fb <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/Fibroblast.super_processed_filtered_annotated_sample.rds")

seu_cc_full <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/Ovarian.cancer.super_processed_filtered_annotated.rds")
seu_tc_full <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/T.super_processed_filtered_annotated.rds")
seu_ml_full <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/Myeloid.super_processed_filtered_annotated.rds")
seu_fb_full <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/Fibroblast.super_processed_filtered_annotated.rds")

seu_cc_full@assays$RNA <- CreateAssayObject(seu_cc_full@assays$RNA@counts)
seu_tc_full@assays$RNA <- CreateAssayObject(seu_tc_full@assays$RNA@counts)
seu_ml_full@assays$RNA <- CreateAssayObject(seu_ml_full@assays$RNA@counts)
seu_fb_full@assays$RNA <- CreateAssayObject(seu_fb_full@assays$RNA@counts)

Idents(seu_cc) <- seu_cc$cluster_label
Idents(seu_tc) <- seu_tc$cluster_label
Idents(seu_ml) <- seu_ml$cluster_label
Idents(seu_fb) <- seu_fb$cluster_label

seu_ml$cell_type <- "Myeloid.cell"
seu_ml_full$cell_type <- "Myeloid.cell"

seu_cc$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_cc$sample]
seu_tc$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_tc$sample]
seu_ml$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_ml$sample]
seu_fb$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_fb$sample]

seu_cc_full$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_cc_full$sample]
seu_tc_full$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_tc_full$sample]
seu_ml_full$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_ml_full$sample]
seu_fb_full$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_fb_full$sample]

seu_merge <- seu_cc %>% 
  merge(seu_tc) %>% 
  merge(seu_ml) %>% 
  merge(seu_fb)

seu_merge_full <- seu_cc_full %>% 
  merge(seu_tc_full) %>% 
  merge(seu_ml_full) %>% 
  merge(seu_fb_full)

seu_merge_full$consensus_signature <- deframe(select(meta_tbl, sample, consensus_signature))[seu_merge_full$sample]

```


```{r chunk_050}

ligand_target_matrix <- read_rds(url("https://zenodo.org/record/3260758/files/ligand_target_matrix.rds"))
lr_network <- read_rds(url("https://zenodo.org/record/3260758/files/lr_network.rds"))
weighted_networks <- read_rds(url("https://zenodo.org/record/3260758/files/weighted_networks.rds"))

```

# Differential interactions per mutational signature

```{r chunk_060}

nichenet_wrapper <- function(cloi1, cloi2, cond1, cond2) {
  tryCatch(nichenet_seuratobj_aggregate(
    seurat_obj = seu_merge, 
    receiver = cloi2, 
    condition_colname = "consensus_signature", 
    condition_oi = cond1, 
    condition_reference = cond2,
    sender = cloi1, 
    ligand_target_matrix = ligand_target_matrix, 
    lr_network = lr_network, 
    weighted_networks = weighted_networks, 
    organism = "human"
  ), error = function(e) NA)
}

nichenet_wrapper_comps <- function(cloi1, cloi2) {
  list(
    HRD_Dup_FBI = nichenet_wrapper(cloi1, cloi2, "HRD-Dup", "FBI"),
    HRD_Dup_HRD_Del = nichenet_wrapper(cloi1, cloi2, "HRD-Dup", "HRD-Del"),
    HRD_Del_FBI = nichenet_wrapper(cloi1, cloi2, "HRD-Del", "FBI")
  )
}

## one receiver against all senders --------------------------------------

# Idents(seu_merge) <- seu_merge$cell_type
# cluster_labels <- sort(unique(seu_merge$cell_type))
# 
# nichenet_output_cell_type <- lapply(cluster_labels, function(x) nichenet_wrapper_comps("all", x)) %>%
#   setNames(cluster_labels)
# write_rds(nichenet_output_cell_type, "/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cell_type.rds")
# 
# Idents(seu_merge) <- seu_merge$cluster_label
# cluster_labels <- sort(unique(seu_merge$cluster_label))
# 
# nichenet_output_cluster_label <- lapply(cluster_labels, function(x) nichenet_wrapper_comps("all", x)) %>%
#   setNames(cluster_labels)
# write_rds(nichenet_output_cluster_label, "/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cluster_label.rds")
 
nichenet_output_cell_type <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cell_type.rds")
nichenet_output_cluster_label <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cluster_label.rds")

## pairwise receiver sender comparisons --------------------------------------

# Idents(seu_merge) <- seu_merge$cell_type
# cluster_labels <- sort(unique(seu_merge$cell_type))
# 
# nichenet_output_cell_type_pw <- parallel::mclapply(cluster_labels, function(x) lapply(cluster_labels, function(y) nichenet_wrapper_comps(x, y)) %>%
#   setNames(cluster_labels), mc.cores = 32) %>% 
#   setNames(cluster_labels)
# write_rds(nichenet_output_cell_type_pw, "/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cell_type_pairwise.rds")
# 
# Idents(seu_merge) <- seu_merge$cluster_label
# cluster_labels <- sort(unique(seu_merge$cluster_label))
# 
# nichenet_output_cluster_label_pw <- parallel::mclapply(cluster_labels, function(x) lapply(cluster_labels, function(y) nichenet_wrapper_comps(x, y)) %>%
#   setNames(cluster_labels), mc.cores = 8) %>%
#   setNames(cluster_labels)
# write_rds(nichenet_output_cluster_label_pw, "/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cluster_label_pairwise.rds")

nichenet_output_cell_type_pw <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cell_type_pairwise.rds")
#nichenet_output_cluster_label_pw <- read_rds("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/nichenet_output_cluster_label_pairwise.rds")

```


# Baseline interactions 

1. what ligands and receptors are expressed in a given cell type for a given patient?

```{r chunk_100}

lr_network_bf <- read_tsv("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/lr_network_bonafide.tsv")

lr_network_pd1 <- filter(lr_network, from == "CD274" | to == "PDCD1") %>% 
  select(ligand = from, receptor = to)

meta_data <- as_tibble(FetchData(seu_merge_full, c("cell_id", "patient_id", "cluster_label", "cell_type", "consensus_signature")))

wrangel_wrapper <- . %>% 
  as.matrix %>% 
  t %>% 
  as.data.frame %>% 
  as_tibble(rownames = "cell_id") %>% 
  gather(gene, value, -cell_id) %>% 
  left_join(meta_data, by = "cell_id")

lig_data <- seu_merge_full@assays$RNA@counts[rownames(seu_merge_full)[rownames(seu_merge_full) %in% unique(lr_network_pd1$ligand)],] %>% 
  wrangel_wrapper
  
lig_summary <- lig_data %>% 
  group_by(patient_id, consensus_signature, gene, cluster_label, cell_type) %>% 
  filter(length(value) > 10) %>% 
  summarise(pct.lig = sum(value > 0)/length(value)) %>% 
  rename(ligand = gene, sender = cluster_label, ct_sender = cell_type) %>% 
  filter(pct.lig > 0.1) %>% 
  ungroup

rec_data <- seu_merge_full@assays$RNA@counts[rownames(seu_merge_full)[rownames(seu_merge_full) %in% unique(lr_network_pd1$receptor)],] %>% 
  wrangel_wrapper
  
rec_summary <- rec_data %>% 
  group_by(patient_id, consensus_signature, gene, cluster_label, cell_type) %>% 
  filter(length(value) > 10) %>% 
  summarise(pct.rec = sum(value > 0)/length(value)) %>% 
  rename(receptor = gene, receiver = cluster_label, ct_receiver = cell_type) %>% 
  filter(pct.rec > 0.1) %>% 
  ungroup

lr_spectrum <- lig_summary %>% 
  left_join(lr_network_pd1, by = "ligand") %>% 
  left_join(rec_summary, by = c("receptor", "patient_id", "consensus_signature")) %>% 
  na.omit

lr_spectrum_summary <- lr_spectrum %>% 
  group_by(patient_id, consensus_signature, sender, receiver, ct_sender, ct_receiver) %>% 
  tally %>% 
  group_by(consensus_signature, sender, receiver, ct_sender, ct_receiver) %>% 
  summarise(mean_n = mean(n))

write_tsv(lr_spectrum, "/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/lr_network_spectrum_pd1.tsv")
write_tsv(lr_spectrum_summary, "/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/nichenet/lr_network_spectrum_summary_pd1.tsv")

# p1 <- ggplot(filter(lr_spectrum_summary, consensus_signature == "HRD-Dup"), 
#              aes(sender, receiver, fill = mean_n)) + 
#   geom_tile() +
#   facet_grid(ct_receiver~ct_sender, scales = "free", space = "free") + 
#   scale_fill_viridis()
# 
# p2 <- p1 %+% filter(lr_spectrum_summary, consensus_signature == "HRD-Del")
# p3 <- p1 %+% filter(lr_spectrum_summary, consensus_signature == "FBI")
# 
# 
# plot_grid(p1, p2, p3, ncol = 3)
# 
# ggplot(lr_spectrum_summary, 
#        aes(sender, receiver, fill = mean_n)) + 
#   geom_tile() +
#   facet_grid(ct_receiver~consensus_signature, scales = "free", space = "free") + 
#   scale_fill_viridis() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
#         axis.ticks.x = element_blank())

```

1. Which ligand can best explain an observed receiver cell state (target gene program)?
2. In which sender cell type is this ligand expressed.
3. What's the most likely receptor binding the ligand on the receiver cell

```{r chunk_200}

marker_tbl <- bind_rows(read_tsv("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/supplementary_tables/Fibroblast.super_marker_table_annotated.tsv"),
read_tsv("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/supplementary_tables/Myeloid.super_marker_table_annotated.tsv"),
read_tsv("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/supplementary_tables/Ovarian.cancer.super_marker_table_annotated.tsv"),
read_tsv("/work/shah/uhlitzf/data/SPECTRUM/freeze/v7/supplementary_tables/T.super_marker_table_annotated.tsv"))

marker_tbl

```




